### 2021-08-30 manuscript/synthetic_data.tex
Synthetic_data.tex + figures.tex ===> Modifiquei os testes sintéticos com grid regular e irregular 10% e seus respectivos captions.

The synthetic data application of the fast equivalent layer for magnetic data was conducted on a regular grid of  $80 \times 80$ points, totaling $N = 6,\, 400$ observation points. Three bodies were modeled: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2\sqrt{2}$ A/m, respectively. The main field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively. Figure \ref{fig:model_mag_synthetic}a shows the synthetic data created for this test.

Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in figure \ref{fig:predicted_synthetic_mag}a. The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_synthetic_mag}a), with mean $0.3712$ nT and standart deviation of $0.2798$ nT is shown in figure \ref{fig:predicted_synthetic_mag}b. This process took $17.10$ seconds.

Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in figure \ref{fig:predicted_bccb_mag}a. The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_bccb_mag}a), with mean $0.5150$ nT and standart deviation of $0.4363$ nT is shown in figure \ref{fig:predicted_bccb_mag}b. This process took $0.18$ seconds.

In figure \ref{fig:convergence_synthetic_mag} we have the convergence analysis of the CGLS method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$ used for this synthetic test. The squared euclidian norm of residuals decreases as expected, with good results at 50 iterations, stabilizing afterwards. This result shows that it is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources.

@@

As shown in theory, a regular grid of observation points is needed to arise the BTTB matrix. In this section, we show the results when this algorithm is used directly into irregular grids of $N = 5 \, 000$ observation points. 
First, we set up a regular grid of $100 \times 50$ observation points in the $x$- and $y$-directions with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of
$163.265$ m along the $y$-axis. Next, the $x$ and $y$ coordinates of the observations were also contaminated with pseudorandom Gaussian noise with zero mean and standard deviations of $10\%$, $30\%$ and $50\%$ of the $\Delta x$ and $\Delta y$ spacing.

Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-direction of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_10}a) has mean $0.3628$ nT, standart deviation of $0.2727$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_10}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_10}a) has mean $0.6024$ nT, standart deviation of $0.4998$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_10}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.

>>>>

The synthetic data application of the fast equivalent layer for magnetic data was conducted on a regular grid of  $80 \times 80$ points, totaling $N = 6,\, 400$ observation points. Three bodies were modeled: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2\sqrt{2}$ A/m, respectively. The main field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively. Figure \ref{fig:model_mag_synthetic} shows the synthetic data created for this test.

Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in Figure \ref{fig:predicted_synthetic_mag}a. The data residuals,  defined as the difference between the observed (Figure \ref{fig:model_mag_synthetic}) and the predicted data 
(Figure \ref{fig:predicted_synthetic_mag}a), with mean of $0.3712$ nT and standart deviation of $0.2798$ nT are shown in Figure \ref{fig:predicted_synthetic_mag}b. This process took $17.10$ seconds.

Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in Figure \ref{fig:predicted_bccb_mag}a. The data residuals, defined as the difference  between the observed (Figure \ref{fig:model_mag_synthetic}) and the predicted data (Figure \ref{fig:predicted_bccb_mag}a), with mean of $0.5150$ nT and standart deviation of $0.4363$ nT is shown in Figure \ref{fig:predicted_bccb_mag}b. 
This process took $0.18$ seconds.

Figure \ref{fig:convergence_synthetic_mag} shows the convergence of our method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$. 
The squared Euclidean norm of the data residuals decreases as expected when the
convergence criterion was satisfied, close to iteration 50. 
This result shows that, in practice, it is not necessary to run the conjugate gradient least square method at $N$ iterations to get an exactly solution.
Actually, the exactly solution  would never occur due to roundoff errors.
Hence, by setting the convergence to  $N$ iterations besides being unnecessary it also demands large computer processing time, even in this synthetic test with a small layer 
($N = 6,\, 400$ equivalent sources).

@@

As shown in the methodology, a regular grid of observation points is needed to arise the BTTB matrix. In this section, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points. 
First, we set up a regular grid of $100 \times 50$ observation points in the $x$- and $y$-directions with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of
$163.265$ m along the $y$-axis. Next, the $x$ and $y$ coordinates of the observations were also contaminated with pseudorandom Gaussian noise with zero mean and standard deviations of $10\%$, $30\%$ and $50\%$ of the 
$\Delta x$ and $\Delta y$ spacing.

Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-direction of the observation points. 
By using the classical approach, Figure \ref{fig:predicted_synthetic_mag_irregular_10}b shows the data residuals,  defined as the difference between the observed  (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_synthetic_mag_irregular_10}a), with mean of $0.3628$ nT, standart deviation of $0.2727$ nT. 
By using our method, Figure \ref{fig:predicted_bccb_mag_irregular_10}b shows the data residuals, difference between the observed (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_bccb_mag_irregular_10}a), with mean of $0.6024$ nT and standart deviation of $0.4998$ nT.
Figure \ref{fig:convergence_synthetic_mag_irregular_10} shows the convergence of our method in which the squared Euclidean norm decreases until it achieves an invariance close to iteration 50.
